### 2021-04-20 paper/ase21/overview.tex
Revised Sec. 2

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{img/overall}
  \caption{Overall structure of $\tool$: a type analyzer and a bug detector for
  mechanized specifications extracted from ECMAScript by $\jiset$.}
  \label{fig:overall}
  \vspace*{-1.5em}
\end{figure}

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{img/example}
  \vspace*{-1.5em}
  \caption{An example JavaScript program with related previous specification
  bugs and their bugfixes.}
  \label{fig:example}
  \vspace*{-1.5em}
\end{figure*}
% XXX
% \begin{lstlisting}[style=FigureJS]
% let f;    f ??= (x) => Math.round(x);    f(true);
% \end{lstlisting}

In this section, we demonstrate overall structure of $\tool$ depicted in
Figure~\ref{fig:overall}.  Our tool consists of three different steps:
1) specification extraction, 2) type analysis, and 3) bug detection.

\subsection{Specification Extraction}\label{sec:overview-spec-extract}

ECMAScript describes JavaScript syntax and semantics written in a structured
natural language.  We utilize $\jiset$ to extract mechanized specification from
a given ECMAScript.

\paragraph{Syntax and Semantics} ECMAScript uses a variant of extended BNF
notations to describe JavaScript syntax.  $\jiset$ synthesizes AST structures
and JavaScript parsers from its lexical and syntactic productions.  Our tool
utilizes only AST structures to define their types and to access corresponding
syntax-directed algorithms.  For JavaScript semantics, ECMAScript contains
abstract algorithms written in a structured natural language.  $\jiset$ compiles
them to functions of $\ires$, an untyped intermediate representation for
ECMAScript.  We modify $\ires$ to make it more suitable for type analysis, and
formally define its syntax and semantics in Section~\ref{sec:ires}.

\paragraph{Types} In ECMAScript, types denote not only JavaScript types but also
specification types for ASTs, records, and lists.  In abstract algorithms, ASTs
are also values thus they can be stored in the variables or passed as arguments.
For such ASTs, we use their production names as their types and automatically
link corresponding syntax-directed algorithms to them as their fields.
ECMAScript also supports various record types and their fields and possible
values are defined in the corresponding tables.  For example, ``Table 9:
Completion Record Fields'' in the latest ECMAScript describes fields of the
completion records.  The latest version contains tens of tables for record types
but they are backward compatible in general.  Thus, we manually model fields of
record types based on the latest version to use them in type analysis.  For
lists, we define the empty list type $\clist{}$ and parametric list types
$\clist{\tau}$.

@@

The type analyzer performs type analysis with flow-sensitivity and
type-sensitivity for parameters to precisely detect specification bugs.  It
consists of two sub-modules: an \textit{analysis initializer} and an
\textit{abstract transfer}.  We use a stack-based worklist algorithm to
calculate fixpoint of abstract transfer and assign the initial set of worklist
using analysis initializer.

\paragraph{Analysis Initializer} In ECMAScript, there are three different kinds
of abstract algorithms \textit{normal}, \textit{syntax-directed} and
\textit{built-in}.  Since all the parameter types are known for built-in
algorithms and syntax-directed algorithms having no additional parameters, we
utilize them as entry points of type analysis.  For each entry point, the
initializer defines its abstract environment with parameter types and push the
pair of entry point and its abstract environment to the worklist.

\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
pair of a control point and its abstract environment from the worklist, produces
other pairs based on abstract semantics, and pushes them to the worklist.  The
iteration will be finished when the worklist becomes empty.  Moreover, to reduce
false alarms by increasing the analysis precision, we perform refinement for
abstract environment when the current control point is a branch or an assertion.
The refinement will be described in detail in Section~\ref{sec:refine}.

@@

To detect specification bugs based on the result of type analysis, we develop
four different checkers in the bug detector.  We explain targets of checkers
using an example JavaScript program with related previous specification bugs and
their bugfixes descirbed in Figure~\ref{fig:example}.

\paragraph{Reference Checker} The example JavaScript program first defines a
variable \jscode{f} without initialization thus it stores \jscode{undefined}.
Then, it assigns an arrow function to \jscode{f} using the operator
\jscode{??=}.  While the corresponding \textbf{Evaluation} algorithm originally
used \textbf{GetReferencedName} algorithm to get reference name at line 4.a, a
contributor removed the \textbf{GetReferencedName} algorithm and replaced its
all invocations to accesses of the field [[ReferencedName]] on October 28, 2020.
However, there were several missing cases including the semantics of
\jscode{??=} until another contributor fixed this bug on November 3, 2020.
Thus, an unknown variable bug of \textbf{GetReferencedName} lated for 6 days.
The reference checker detects reference bugs including unknown variable bugs.

\paragraph{Arity Checker} After the program assigns an arrow function to
\jscode{f}, it calls the function with an argument \jscode{true}.  During the
initialization of a function call, the \textbf{IteratorBindingInitialization}
algorithm is evaluated with additional parameters \textit{iteratorRecord} and
\textit{environment} to assigns arguments to proper parameters.  However, a
contributor missed the additional parameters at line 2 in the
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September
6, 2018.  It caused an arity mismatch bug and lasted for 532 days until another
contributor fixed this bug on February 20, 2020.  The arity checker checks such
arity mismatches.

\paragraph{Assertion Checker} During the initialization of the function call,
another specification bug existed in \textbf{IteratorBindingInitialization} of
\textit{FormalParameter}.  The additional \textit{environment} parameter might
contains \jscode{undefined} or an environment record exactly same with
\textit{originalEnv} as described in the assertion at line 5.  However, a
contributor initially added the assertion without considering of
\jscode{undefined} on \inred{XXXXXX XX, XXXX}.  Thus, the assertion failure bug
lasted for \inred{XXXX} days until April 10, 2019.  The assertion checker checks
whether such assertions are failed or not.

\paragraph{Operand Checker} The last checker checks whether operand types are
correct for typed operators.  After the function call initialization, the
parameter \jscode{x} points to \jscode{true} thus \jscode{Math.round} is invoked
with the argument \jscode{true}.  The \jscode{Math.round} built-in library
first converts the given parameter \textit{x} to the corresponding number value
\textit{n} using \textbf{ToNumber} algorithm, and then performs remaining steps
using the number value \textit{n}.  However, a contributor made a mistake of
using \textit{x} instead of \textit{n} at line 3 and 4 on September 11 2020.
According to this specification, the specification tries to compare a boolean
value \jscode{true} with a numeric value 0.5 or 0 in the example JavaScript
program.  Fortunately, another contributor fixed this bug after two days.  In
the bug detector, the operand checker detects whether the operand types are
compatible with the typed operators.

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase analysis precision using
refinement (Section~\ref{sec:analyzer}) and how to detect type-related
specification bugs using four different checkers (Section~\ref{sec:checker}).
After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{img/overall}
  \caption{$\tool$: a type analyzer and a bug detector for
  mechanized specifications extracted from ECMAScript by $\jiset$}
  \label{fig:overall}
  \vspace*{-1.5em}
\end{figure}

\begin{figure*}[t]
  \centering
  \includegraphics[width=.9\textwidth]{img/example}
%  \vspace*{-1.5em}
  \caption{An example JavaScript program with related previous specification
  bugs and their bug fixes}
  \label{fig:example}
  \vspace*{-1.5em}
\end{figure*}
% XXX
% \begin{lstlisting}[style=FigureJS]
% let f;    f ??= (x) => Math.round(x);    f(true);
% \end{lstlisting}

In this section, we demonstrate the overall structure of $\tool$ depicted in
Figure~\ref{fig:overall}.  It consists of three components:
1) specification extraction, 2) type analysis, and 3) bug detection.

\subsection{Specification Extraction}\label{sec:overview-spec-extract}
$\tool$ extracts the JavaScript syntax and semantics using $\jiset$,
and it extracts specification types from ECMAScript.

\paragraph{Syntax and Semantics}
ECMAScript uses a variant of extended BNF notations to describe the JavaScript syntax.
While $\jiset$ synthesizes AST structures and JavaScript parsers from
the lexical and syntactic productions in ECMAScript, $\tool$ uses only
AST structures to define their types and access corresponding syntax-directed algorithms.
ECMAScript uses abstract algorithms written in a structured natural language to
describe the JavaScript semantics. While $\jiset$ compiles abstract algorithms to functions in $\ires$,
we modify $\ires$ to make it more suitable for type analysis as
formally defined in Section~\ref{sec:ires}.

\paragraph{Types}
$\tool$ represents three kinds of specification types.
First, because ASTs are values in abstract algorithms, 
they can be stored in variables and passed as function arguments.
For ASTs, we use their production names as their
types and automatically link their corresponding syntax-directed algorithms as their fields.
Second, ECMAScript supports various record types and fields
whose possible values are defined in their corresponding tables.
For example, ``Table 9: Completion Record Fields'' in the latest
ECMAScript describes the fields of the completion records.
% The newest version contains tens of tables for record types, and they are backward compatible in general.
Thus, we manually model the fields of record types based on the tables
in the latest version and use them in a type analysis.
Third, for list-like structures, we define the empty list type
$\clist{}$ and parametric list types $\clist{\tau}$.

@@

$\tool$ performs a type analysis with flow-sensitivity and
type-sensitivity for arguments.
Each function is split into multiple flow- and type-sensitive views, and an
abstract state stores mapping from views to corresponding abstract environments.
To andle views separately, we use a worklist algorithm.
The type analyzer consists of two sub-modules: an \textit{analysis initializer} and an
\textit{abstract transfer}.

\paragraph{Analysis Initializer} It defines the initial abstract state and the
initial set of views for a worklist. ECMAScript provides three
kinds of abstract algorithms: \textit{normal}, \textit{syntax-directed}, and
\textit{built-in}. Since syntax-directed algorithms and built-in algorithms have
their parameter types, we use them as entry points of type analysis.  For each entry point, the
initializer defines its abstract environment with parameter types and adds the
flow- and type-sensitive views of the entry point to the worklist.

\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
specific view from the worklist and udpates the abstract environments of the next
views based on the abstract semantics.  It adds the next views to the worklist if
it changes their abstract environments, and the iteration finishes when
the worklist becomes empty.  To increase the analysis precision, we
perform a condition-based refinement for an abstract environment when the current
control point is a branch or an assertion as described in Section~\ref{sec:refine}.

@@

To detect specification bugs utilizing the type analysis, we develop
four checkers in a bug detector.  We explain the targets of the checkers
with an example JavaScript program that contains related previous specification bugs and
their bug fixes, as shown in Figure~\ref{fig:example}.

\paragraph{Reference Checker} The example JavaScript program first defines a
variable \jscode{f} without initialization, which has the value \jscode{undefined}.
It then assigns an anonymous function to \jscode{f} using the operator \jscode{??=}.
While the corresponding \textbf{Evaluation} algorithm originally
used the \textbf{GetReferencedName} algorithm to get a reference name on line 4.a,
a contributor removed the \textbf{GetReferencedName} algorithm and replaced all its
invocations with accesses of the field [[ReferencedName]] on October 28, 2020.
However, the contributor missed several cases including the semantics of
\jscode{??=}, which was fixed by another contributor on November 3, 2020.
Thus, the unknown variable bug for \textbf{GetReferencedName} existed for 7 days,
which the reference checker can detect.

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, the \textbf{IteratorBindingInitialization}
algorithm executes with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which existed for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

\paragraph{Assertion Checker} During the initialization of the function call,
another specification bug existed in \textbf{IteratorBindingInitialization} of
\textit{FormalParameter}.  The additional \textit{environment} parameter may
contain \jscode{undefined} or an environment record exactly the same as
\textit{originalEnv} as described in the assertion on line 5.
However, the assertion missed that the initial commit
of the open development process on September 22, 2015 introduced
\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.
The assertion checker can detect such assertion failures.

\paragraph{Operand Checker} After the function call initialization, the
parameter \jscode{x} has the value \jscode{true}, and \jscode{Math.round} is invoked
with the argument \jscode{true}.  The \jscode{Math.round} built-in library first
converts the given parameter \textit{x} to its corresponding number value
\textit{n} using \textbf{ToNumber}, and then performs the remaining
steps using \textit{n}.  However, a contributor mistakenly used
\textit{x} instead of \textit{n} on lines 3 and 4 on September 11, 2020.
This bug caused the algorithm to compare the boolean value \jscode{true} with the
numeric value 0.5 or 0 in the example JavaScript program.
This bug lived for two days until another contributor fixed it, and
the operand checker can detect such bugs.

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase the analysis precision using
the condition-based refinement (Section~\ref{sec:analyzer}) and how to detect
type-related specification bugs (Section~\ref{sec:checker}).  After we evaluate $\tool$
(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
and conclude (Section~\ref{sec:conclusion}).
